SU($n$) ferromagnets near the Heisenberg point

### 2020-06-17 collective_sun/sun_perturbation.tex
added appendix about choosing the operator content for excitation energy eigenstates

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\G}{\mathcal{G}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\T}{\mathcal{T}}

@@

In this work, we generalize some of the techniques used to harness
SU(2)-symmetric spin interactions for metrological advantage to the
case of SU($n$).  In doing so, we develop a low-energy effective
theory of gapped SU($n$) ferromagnets with weakly broken SU($n$)
symmetry (e.g.~due to external fields or additional interaction
terms).  The restriction of our theory to ferromagnetic interactions
can be relaxed to the assumption of
\begin{enumerate*}
\item an initial state in the manifold of permutationally-symmetric
  states, a multi-level generalization of the Dicke manifold for
  two-level spins, together with the assumption that
\item this manifold is gapped away from states that break
  permutational symmetry.
\end{enumerate*}
In addition to working out the effective Hamiltonian induced by weak
SU($n$) symmetry breaking through second order in perturbation theory,
we develop a diagrammatic method to systematically compute matrix
elements of arbitrary spin operators within manifolds of weakly broken
permutational symmetry, thereby enabling the numerical simulation of
dynamics induced by non-perturbative modifications to the SU($n$)
Heisenberg model.  While these simulations generally accumulate
uncontrolled errors from the truncation of Hilbert space, we identify
criteria under which numerical results correctly capture the
qualitative dynamical behavior of a system.

@@

In the case of SU(2), the PS manifold $\M_0$ is precisely the {\it
  Dicke manifold} spanned by the PS states $\ket{m_\up,m_\dn}$ with a
definite (integer) number $m_\mu\ge0$ of spins occupying the
single-spin state $\mu\in\set{\up,\dn}$.  If there are $N$ spins
total, then Dicke states $\ket{m_\up,m_\dn}$ must have
$m_\up+m_\dn=N$.  In the case of multi-level spins, the PS manifold
$\M_0$ is similarly spanned by states
$\ket{m}=\ket{m_1,m_2,\cdots,m_n}$ with a definite occupation number
$m_\mu\ge0$ of the single-spin state $\mu$, and $\sum_\mu m_\mu=N$.
These states are essentially labeled by an assignment
$m=\p{m_1,m_2,\cdots,m_n}$ of $N$ (identical) spins to $n$ (distinct)
states.  We denote the set of all such assignments by $\A_n\p{N}$,
such that our standard basis for $\M_0$ is
$\set{\ket{m}:m\in\A_n\p{N}}$.  The dimension of $\M_0$, or
equivalently the ground-state degeneracy of $H_0$, is straightforward
to determine with a standard ``stars and bars'' calculation:
$\dim\p{\M_0}=\abs{\A_n\p{N}} = {N+n-1 \choose n-1} \sim N^{n-1}$.
The energy of any PS state $\ket\psi\in\M_0$ with respect to the
interaction Hamiltonian $H_0$ in \eqref{eq:H_0} is
\begin{align}
  E_0 = \sum_{i<j} h_{ij} = \f12 \sum_{i\ne j} h_{ij}.
\end{align}

@@

\begin{figure}
  \centering
  \includegraphics{structure/mat_L101_a2.pdf}
  \caption{Visualizations of dimension-$r$ tensors $\m w$ that
    generate the lowest-lying (unnormalized) $r$-magnon states
    $\ket{\m w,m} \equiv \O\p{\m w, \sigma_\z^{\otimes{r}}} \ket{m}$
    with definite excitation energy $\Delta$ above the PS manifold
    $\M_0$ of a periodic 1D lattice of $N=101$ spins interacting via
    the SU(2)-symmetric Hamiltonian in \eqref{eq:H_SU2} with power-law
    couplings $h_{ij}=-1/\oper{dist}\p{i,j}^2$.  Here
    $\oper{dist}\p{i,j}\equiv\min\p{\abs{i-j},N-\abs{i-j}}$ is the
    minimal distance between spins $i,j$.  Top row ($r=2$) shows the
    full 2D matrix $\m w = \sum_{i,j}w_{ij}\op{i}{j}$, and bottom row
    ($r=3$) shows a single 2D slice of the full 3D tensor,
    $\tilde{\m w}_0 = \sum_{i,j}w_{ij,0}\op{i}{j}$.  Blue (red) pixels
    correspond to matrix elements with a positive (negative) sign, and
    darker colors indicate larger absolute values.  In the case of
    $r=2$, translational invariance enforces $w_{ij}=w_{i-d,j-d}$ for
    all displacements $d$, so every row of $\m w$ is some translation
    of a single (arbitrary) row.  Similarly, when $r=3$ every 2D slice
    of the full 3D tensor can be obtained by appropriately translating
    the 2D slice $\tilde{\m w}_0$ shown above.  In the case of SU($n$)
    with $n>2$, the ``$r$-magnon'' excitation energies $\Delta$ and
    tensors $\m w$ remain identical, but now correspond to a
    degenerate set of states that are generated by different choices
    of $r$-body operators in place of $\sigma_\z^{\otimes r}$.}
  \label{fig:structure}
\end{figure}

@@

In the case of an SU($n$) spin system, we can similarly start with the
ground-state PS manifold
$\M_0=\oper{span}\set{\ket{m}:m\in\A_n\p{N}}$, and generate excited
states by the action of multi-body operators, $\O\p{\m w,X}\ket{m}$.
The choice of tensors $\m w$ for generating states in the $r$-magnon
manifold $\M_r$ is the same as before, but we now have the additional
complication of having to choose $r$-spin operators, $X$.  As with the
choice of $\sigma_\z^{\otimes r}$ for SU(2), it suffices to choose
tensor products of {\it diagonal} single-spin operators (that is,
diagonal in a fixed single-particle basis), but there will now be
$\sim\p{n-1}^r$ distinct choices that generate degenerate, orthogonal
states: one of $n-1$ diagonal operators (that are linearly independent
of each other and the identity) for each of $r$ tensor factors.  We
discuss the exact choice of operators in more detail in Appendix
\ref{sec:operator_content}.  To summarize, for each PS state
$\ket{m}$, we identify a basis $\set{Z_{m\nu}:\nu\in\ZZ_{n-1}}$ of
single-spin operators that are diagonal and linearly independent of
the identity, and choose a list of integers
$z\equiv\p{z_1,z_2,\cdots,z_{n-1}}\in\A_{n-1}\p{r}$ to define the
$r$-spin operator
\begin{align}
  X_{mz} \equiv \bigotimes_{\nu=1}^{n-1} Z_{m\nu}^{\otimes z_\nu}
  = \underbrace{Z_{m,1} \otimes \cdots \otimes Z_{m,1}}_{z_1~\t{times}}
  \otimes
  \underbrace{Z_{m,2} \otimes \cdots \otimes Z_{m,2}}_{z_2~\t{times}}
  \otimes \cdots \otimes
  \underbrace{Z_{m,n-1} \otimes \cdots
    \otimes Z_{m,n-1}}_{z_{n-1}~\t{times}}.
\end{align}
Our basis for $\M_r$ then consists of the states
$\ket{m,\m w,z}\equiv\O\p{\m w,X_{mz}}\ket{m}$.

@@

\red{[todo: write section]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Permutation-symmetrized products of multi-body operators}
\label{sec:operator_product}

>>>>

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\G}{\mathcal{G}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\R}{\mathcal{R}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\Z}{\mathcal{Z}}

@@

In this work, we generalize some of the techniques used to harness
SU(2)-symmetric spin interactions for metrological advantage to the
case of SU($n$).  In doing so, we develop a low-energy effective
theory of gapped SU($n$) ferromagnets with weakly broken SU($n$)
symmetry (e.g.~due to external fields or additional interaction
terms).  The restriction of our theory to ferromagnetic interactions
can be relaxed to the assumption of
\begin{enumerate*}
\item an initial state in the manifold of permutationally-symmetric
  states, a multilevel generalization of the Dicke manifold for
  two-level spins, together with the assumption that
\item this manifold is gapped away from states that break
  permutational symmetry.
\end{enumerate*}
In addition to working out the effective Hamiltonian induced by weak
SU($n$) symmetry breaking through second order in perturbation theory,
we develop a diagrammatic method to systematically compute matrix
elements of arbitrary spin operators within manifolds of weakly broken
permutational symmetry, thereby enabling the numerical simulation of
dynamics induced by non-perturbative modifications to the SU($n$)
Heisenberg model.  While these simulations generally accumulate
uncontrolled errors from the truncation of Hilbert space, we identify
criteria under which numerical results correctly capture the
qualitative dynamical behavior of a system.

@@

In the case of SU(2), the PS manifold $\M_0$ is precisely the {\it
  Dicke manifold} spanned by the PS states $\ket{m_\up,m_\dn}$ with a
definite (integer) number $m_\mu\ge0$ of spins occupying the
single-spin state $\mu\in\set{\up,\dn}$.  If there are $N$ spins
total, then Dicke states $\ket{m_\up,m_\dn}$ must have
$m_\up+m_\dn=N$.  In the case of multilevel spins, the PS manifold
$\M_0$ is similarly spanned by states
$\ket{m}=\ket{m_1,m_2,\cdots,m_n}$ with a definite occupation number
$m_\mu\ge0$ of the single-spin state $\mu$, and $\sum_\mu m_\mu=N$.
These states are essentially labeled by an assignment
$m=\p{m_1,m_2,\cdots,m_n}$ of $N$ (identical) spins to $n$ (distinct)
states.  We denote the set of all such assignments by $\A_n\p{N}$,
such that our standard basis for $\M_0$ is
$\set{\ket{m}:m\in\A_n\p{N}}$.  The dimension of $\M_0$, or
equivalently the ground-state degeneracy of $H_0$, is straightforward
to determine with a standard ``stars and bars'' calculation:
$\dim\p{\M_0}=\abs{\A_n\p{N}} = {N+n-1 \choose n-1} \sim N^{n-1}$.
The energy of any PS state $\ket\psi\in\M_0$ with respect to the
interaction Hamiltonian $H_0$ in \eqref{eq:H_0} is
\begin{align}
  E_0 = \sum_{i<j} h_{ij} = \f12 \sum_{i\ne j} h_{ij}.
\end{align}

@@

\begin{figure}
  \centering
  \includegraphics{structure/mat_L101_a2.pdf}
  \caption{Visualizations of dimension-$r$ tensors $\m w$ that
    generate the lowest-lying (unnormalized) $r$-magnon states
    $\ket{\m w,m} \equiv \O\p{\m w, \sigma_\z^{\otimes{r}}} \ket{m}$
    with definite excitation energy $\Delta$ above the PS manifold
    $\M_0$ in a periodic 1D lattice of $N=101$ spins interacting via
    the SU(2)-symmetric Hamiltonian in \eqref{eq:H_SU2} with power-law
    couplings $h_{ij}=-1/\oper{dist}\p{i,j}^2$.  Here
    $\oper{dist}\p{i,j}\equiv\min\p{\abs{i-j},N-\abs{i-j}}$ is the
    minimal distance between spins $i,j$.  Top row ($r=2$) shows the
    full 2D matrix $\m w = \sum_{i,j}w_{ij}\op{i}{j}$, and bottom row
    ($r=3$) shows a single 2D slice of the full 3D tensor,
    $\tilde{\m w}_0 = \sum_{i,j}w_{ij,0}\op{i}{j}$.  Blue (red) pixels
    correspond to matrix elements with a positive (negative) sign, and
    darker colors indicate larger absolute values.  In the case of
    $r=2$, translational invariance enforces $w_{ij}=w_{i-d,j-d}$ for
    all displacements $d$, so every row of $\m w$ is some translation
    of a single (arbitrary) row.  Similarly, when $r=3$ every 2D slice
    of the full 3D tensor can be obtained by appropriately translating
    the 2D slice $\tilde{\m w}_0$ shown above.  In the case of SU($n$)
    with $n>2$, the ``$r$-magnon'' excitation energies $\Delta$ and
    tensors $\m w$ remain identical, but now correspond to a
    degenerate set of states that are generated by different choices
    of $r$-body operators in place of $\sigma_\z^{\otimes r}$.}
  \label{fig:structure}
\end{figure}

@@

In the case of an SU($n$) spin system, we can similarly start with the
ground-state PS manifold
$\M_0=\oper{span}\set{\ket{m}:m\in\A_n\p{N}}$, and generate excited
states by the action of multi-body operators, $\O\p{\m w,X}\ket{m}$.
The choice of tensors $\m w$ for generating states in the $r$-magnon
manifold $\M_r$ is the same as before, but we now have the additional
complication of having to choose $r$-spin operators, $X$.  As with the
choice of $\sigma_\z^{\otimes r}$ for SU(2), it suffices to choose
tensor products of {\it diagonal} single-spin operators (that is,
diagonal in a fixed single-particle basis), but there will now be
$\sim\p{n-1}^r$ choices: one of $n-1$ diagonal operators (that are
linearly independent of the identity) for each of $r$ tensor factors.
We discuss the exact choice of operators in more detail in Appendix
\ref{sec:operator_content}.  To summarize, we define $n$ single-spin
operators $Z_\nu\equiv1-2\op\nu=\sum_{\mu\ne\nu}\op\mu-\op\nu$, for
which $Z_\nu=\pm\sigma_\z$ in the case of SU(2), and we choose a list
of non-negative integers $z\equiv\p{z_1,z_2,\cdots,z_n}$ with
$\sum_\mu z_\mu=r$ to define the $r$-spin operator
\begin{align}
  X_z \equiv \bigotimes_{\nu=1}^n Z_\nu^{\otimes z_\nu}
  = \underbrace{Z_1 \otimes \cdots \otimes Z_1}_{z_1~\t{times}}
  \otimes
  \underbrace{Z_2 \otimes \cdots \otimes Z_2}_{z_2~\t{times}}
  \otimes \cdots \otimes
  \underbrace{Z_n \otimes \cdots \otimes Z_n}_{z_n~\t{times}}.
\end{align}
Our starting basis for $\M_r$ then consists of states
$\ket{m,\m w,z}\equiv\O\p{\m w,X_z}\ket{m}$, where we enforce that
$z_\nu\le m_\nu$ for all $\nu$ (where $m_\nu$ is the occupation number
of the single-spin state $\nu$), and that $z$ is zero in an entry
where $m$ is maximal: $z_\nu=0$ for
$\nu=\min\set{\mu:m_\mu=\max\p{m}}$.  This second restriction is
equivalent to removing an operator from $\set{Z_\nu:\nu\in\ZZ_n}$,
making the remaining set linearly independent of the identity
operator.  The basis $\set{\ket{m,\m w,z}}$ for $\M_r$ is generally
complete, but {\it not} orthonormal, so as a final step we construct
an orthonormal basis $\set{\ket{m,\m w,X}}$, where for operators $X$
we define $\ket{m,\m w,X}\equiv\O\p{\m w,X}\ket{m}$ (see Appendix
\ref{sec:operator_content}).

@@

Throughout our construction of excitation energy eigenstates of the
form $\O\p{\m w,X}\ket\psi$, where $\ket\psi\in\M_0$ is a PS state, we
have thus far primarily considered the choice of scalar coefficients,
$\m w$.  Here, we discuss the choice of operators, $X$, which allows
us to construct a complete and convenient basis for the set of all
excited states.  Our construction of a basis for the set of excited
states begins with the standard basis $\set{\ket{m}:m\in\A_n\p{N}}$
for the PS manifold $\M_0$, where $m\equiv\p{m_1,m_2,\cdots,m_n}$ and
$m_\mu$ is the (integer) occupation number of the single-spin state
$\mu$.  Written in the ``computational basis'' of $N$ multilevel
spins, these states are
\begin{align}
  \ket{m} =
  \f1{\sqrt{\C\p{m}}}
  \sum_{\substack{\t{distinct}\\\t{permutations}\\\Pi~\t{of}~\tilde m}}
  \Pi \ket{\tilde m},
  &&
  \ket{\tilde m} \equiv \bigotimes_\mu \ket{\mu}^{\otimes m_\mu},
  \label{eq:pops_expansion}
\end{align}
where $\C\p{m}$ is a normalization factor equal to the number of terms
in the sum.  The basic idea in constructing a basis for the set of
excited states is to find a set of operators that give us control over
the signs of the terms in the expansion above, which is sufficient
control to generate {\it any} state that is consistent with the
populations $m$.  Framing the problem of generating excited states as
one of controlling signs in \eqref{eq:pops_expansion} makes it clear
that we can freely restrict ourselves to considering only operators
that are $\pm1$ on the diagonal (and zero elsewhere) in the
computational basis.

The set of all operators that are $\pm1$ on the diagonal (in the
computational basis) is spanned by sums and tensor products of the
single-spin operators
$Z_\nu\equiv1-2\op\nu=\sum_{\mu\ne\nu}\op\mu-\op\nu$.  Given a list of
non-negative integers $z\equiv\p{z_1,z_2,\cdots,z_n}$ with
$\sum_\mu z_\mu=r$, we thus define the $r$-spin operator
\begin{align}
  X_z \equiv \bigotimes_\mu Z_\mu^{z_\mu},
\end{align}
and nominally use states of the form
$\ket{m,\m w,z}=\O\p{\m w,X_z}\ket{m}$ as our basis for the $r$-magnon
manifold $\M_r$.  There are three points to address concerning the
states $\ket{m,\m w,z}$:
\begin{enumerate*}
\item depending on the value of $m$, some choices of $z$ result in
  trivial states, $\ket{m,\m w,z}=0$;
  \label{pt:trivial}
\item the set of nontrivial states is generally overcomplete, in that
  any given state can be written as a nontrivial linear combination of
  others, and finally
  \label{pt:dependent}
\item even after identifying a linearly independent set of nontrivial
  states, any given pair of states $\ket{m,\m w,y},\ket{m,\m w,z}$
  with $y\ne z$ generally have a non-zero overlap, which is to say
  that they are not orthogonal.
  \label{pt:orthogonal}
\end{enumerate*}
To address the first two points, \ref{pt:trivial} and
\ref{pt:dependent}, we will place restrictions on the values of $z$
that we allow for any given $m$.  The last point, \ref{pt:orthogonal},
will require us to construct a basis of orthonormal states numerically
for any given values of $m,\m w$.

First, we identify criteria under which we are guaranteed that
$\ket{m,\m w,z}=0$.  We begin by assuming that $\ket{m,\m w,z}\in\M_r$
with $\sum_\nu z_\nu=r$.  We then observe that if $z_\nu>m_\nu$, then
$m_\nu-z_\nu$ factors of $Z_\nu$ in $X_z$ are ``wasted,'' in the sense
that they never yield relative signs in different terms of $\ket{m}$
when expressed in the computational basis, as in
\eqref{eq:pops_expansion}.  More concretely, consider the individual
terms of the expansion
\begin{align}
  \ket{m,\m w,z}
  = \f1{\sqrt{\C\p{m}}}
  \sum_{\substack{\t{distinct}\\\t{permutations}\\\Pi~\t{of}~\tilde m}}
  \sum_{k\in\D_N\p{r}} w_k \sp{X_z}_k \Pi \ket{\tilde m},
  \label{eq:excited_state_expansion}
\end{align}
where $\sp{X_z}_k$ denotes the action of $X_z$ on spins
$k=\p{k_1,k_2,\cdots,k_r}$.  All terms in
\eqref{eq:excited_state_expansion} have exactly $m_\nu$ spins in the
state $\nu$.  For any fixed $k$, at least $m_\nu-z_\nu$ factors of
$Z_\nu$ in $\sp{X_z}_k$ must therefore evaluate to $+1$.  We can
eliminate these ``extra'' factors of $Z_\nu$ by replacing
$m_\nu-z_\nu$ of the factors that evaluate to $+1$ by the identity
operator.  Performing this replacement for all $\nu\in\ZZ_n$ yields a
state $\ket{m,\m w_{mz},{\floor{z}_m}}=\ket{m,\m w,z}$, where
$\floor{z}_m\equiv\p{\min\set{z_\nu,m_\nu}:\nu\in\ZZ_n}$ indexes the
$q$-spin operator $X_{\floor{z}_m}$, and $\m w_{mz}$ is some new
tensor of coefficients.  If $q<r$ (because $z_\nu>m_\nu$ for some
$\nu$), then our initial assumption that $\ket{m,\m w,z}\in\M_r$
implies that $\ket{m,\m w,z}=0$.  In other words, a nontrivial basis
$\set{\ket{m,\m w,z}}$ for $\M_r$ must have $z_\nu\le m_\nu$ for all
$\nu$.

Next, we address the fact that the basis $\set{\ket{m,\m w,z}}$ for
$\M_r$ is overcomplete.  This fact is a simple consequence of our
choice of single-spin operators for the construction of
$\ket{m,\m w,z}$, namely $\set{Z_\nu:\nu\in\ZZ_n}$.  In essence, our
problem is the fact that $Z_\nu=\p{n-2}-\sum_{\mu\ne\nu}Z_\mu$, which
implies that any state $\ket{m,\m w,z}\in\M_r$ can be written as a
linear combination of states in which $z_\nu\to z_\nu-1$, and possibly
$z_\mu\to z_\mu+1$ for some $\mu$.  We can eliminate this redundancy
by removing an operator from the $\set{Z_\nu}$, or equivalently
enforcing that $z_\nu=0$ for some $\nu$.  As a matter of choice, we
therefore consider only states $\ket{m,\m w,z}$ for which $z$ is zero
at the first entry where $m$ is maximal: $z_\nu=0$ for
$\nu=\min\set{\mu:m_\mu=\max\p{m}}$.  Given our previous restriction
that $z_\nu\le m_\nu$ for all $\nu$, enforcing that $z$ is zero at an
entry where $m$ is maximal maximizes the number of candidate values of
$z$ that we eliminate from consideration.

The above restrictions on $z$ do not {\it guarantee} that
$\ket{m,\m w,z}\ne0$, or that the restricted basis
$\set{\ket{m,\m w,z}}$ for $\M_r$ will not be overcomplete.
Furthermore, this restricted basis is not orthogonal, which is to say
that generally $\bk{m,\m v,y|m,\m w,z}\ne0$ even when $y\ne z$.  In
order to construct an orthonormal basis for $\M_r$, we therefore need
to build a matrix $B_m$ with matrix elements
\begin{align}
  B_m\p{\m v,y;\m w,z} \equiv \bk{m,\m v,y|m,\m w,z},
\end{align}
where $y,z$ satisfy the restrictions outlined above, and $\m v,\m w$
are chosen from the set of tensors that generate eigenstates of $H_0$.
Eigenvectors of $B_m$ are then mutually orthogonal vectors of the form
$\sum_{\m w,z}c_{\m w z}\ket{m,\m w,z}$, whose squared norms are equal
to their corresponding eigenvalues.  Note that the matrix $B_m$ has a
block-diagonal structure, as it cannot (for example) couple states
$\ket{m,\m v,y},\ket{m,\m w,z}$ whose tensors $\m v,\m w$ generate
states with different interaction energies.  We therefore only need to
build and diagonalize this matrix independently within each block.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Products of multi-body operators}
\label{sec:operator_product}
